The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-09-12 paper/mri_paper.tex
fixed annoying bibtex issue... I think

\documentclass[12pt]{emulateapj}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\hyd}    {{\rm H}}
\newcommand{\vobs}{v_{\rm obs}}
\newcommand{\hi}{H{\sc i}~}
\newcommand{\hii}{H{\sc ii}~}
\newcommand{\hia}{H{\sc i}}
\newcommand{\hiia}{H{\sc ii}}

@@

The magnetorotational instability (MRI) is the leading candidate for rapid angular momentum transport in astrophysical disks. The instability arises when a differentially rotating disk is threaded by a vertical magnetic field (\citei{CHANDRASEKHAR:1960wh}). The presence of the magnetic field destabilizes the disk gas, driving turbulence and angular momentum transport.

@@

%\bibliographystyle{yahapj}
\bibliography{mri.bib}

>>>>

\documentclass{emulateapj}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\hyd}    {{\rm H}}
\newcommand{\vobs}{v_{\rm obs}}
\newcommand{\hi}{H{\sc i}~}
\newcommand{\hii}{H{\sc ii}~}
\newcommand{\hia}{H{\sc i}}
\newcommand{\hiia}{H{\sc ii}}

@@

For matter to accrete from disks onto their central objects, some mechanism for angular momentum transport beyond mere molecular viscosity must be invoked. Since its discovery by \citeauthor{Chandrasekhar:1960wh} (\citeyear{Chandrasekhar:1960wh}) and subsequent rediscovery by \citeauthor{Balbus:1991vs} (\citeyear{Balbus:1991vs}), the MRI remains the leading explanation for rapid angular momentum transport in astrophysical disks. The instability arises when a differentially rotating disk is threaded by a vertical magnetic field. The presence of the magnetic field destabilizes the disk gas, driving turbulence and angular momentum transport.

@@

%\bibliographystyle{plain}
%\bibliography{mri_refs2}

\bibliographystyle{plain}

\begin{thebibliography}{53}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{Chandrasekhar(1960)}]{Chandrasekhar:1960wh}
Chandrasekhar, S. 1960, Proceedings of the National Academy of Sciences of the United States of America, 46, 253

\bibitem[{Balbus(1991)}]{Balbus:1991vs}
Balbus, S A and Hawley, J F, The Astrophysical Journal, 376, 214

\end{thebibliography}
